Supporting Information

### 2021-09-03 vertical-thermal-review_SI.Rmd
work on table S1

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
NEON_table <- read.csv("NEON_height_profiles/NEON_sites_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
NEON_table <- NEON_table[c(2:6)] #select and order columns for inclusion
ft <- flextable(NEON_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .75)
ft <- width(ft, 2, width = 2)
ft <- width(ft, 3, width = .5)
ft <- width(ft, 4, width = 1.2)
ft <- width(ft, 5, width = 2)
ft
```

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
NEON_table <- read.csv("NEON_height_profiles/NEON_sites_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
NEON_table <- NEON_table[c(2:4, 6:8)] #select and order columns for inclusion
ft <- flextable(NEON_table)
ft <- autofit(ft)
ft <- width(ft, 1, width = .75)
ft <- width(ft, 2, width = 1.75)
ft <- width(ft, 3, width = .5)
ft <- width(ft, 4, width = .75)
ft <- width(ft, 5, width = .8)
ft <- width(ft, 6, width = 1.75)
ft
```
